Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-11 paper/main.tex
minor

In summary, we make the following \emph{contributions}.
\itemskip
\begin{itemize}
\item We develop the first automatic amortized analysis for C
  programs. It is naturally compositional, tracks size changes of
  variables to derive global bounds, can handle mutually-recursive
  functions, generates resource abstractions for functions, derives
  proof certificates, and handles resources that can
  become available during execution.
\item We show how to automatically reduce the inference of \emph{linear} resource
    bounds to efficient LP solving.
\item We describe a new method of harnessing existing qualitative
  verification techniques to guide the automatic amortized analysis
  to derive \emph{non-linear} resource bounds with LP solving.
\item We prove the soundness of the analysis with respect to a
  parametric cost semantics for C programs. The cost model can be
  further customized with function calls (\code{tick(n)}) that
  indicate resource usage. % This mechanism is also covered by the
  % soundness proof.
\item We present experiments with a prototype implementation on more
  than 2000 lines of C code. A detailed comparison shows that our
  prototype is the only tool that can derive global bounds for larger
  C programs while being as powerful as existing tools when deriving
  linear local bounds for tricky loop and recursion patterns.
\end{itemize}
\itemskip
%
{\footnotesize \sl
[To the reviewers: The auxiliary material contains an anonymized
version of the extended article, and the source code of $\toolname$
and all examples.] }

>>>>

In summary, we make the following \emph{contributions}.
\itemskip
\begin{itemize}
\item We develop the first automatic amortized analysis for C
  programs. It is naturally compositional, tracks size changes of
  variables to derive global bounds, can handle mutually-recursive
  functions, generates resource abstractions for functions, derives
  proof certificates, and handles resources that can
  become available during execution.
\item We show how to automatically reduce the inference of \emph{linear} resource
    bounds to efficient LP solving.
\item We describe a new method of harnessing existing qualitative
  verification techniques to guide the automatic amortized analysis
  to derive \emph{non-linear} resource bounds with LP solving.
\item We prove the soundness of the analysis with respect to a
  parametric cost semantics for C programs. The cost model can be
  further customized with function calls (\code{tick(n)}) that
  indicate resource usage. % This mechanism is also covered by the
  % soundness proof.
\item We present experiments with a prototype implementation on more
  than 2000 lines of C code. A detailed comparison shows that our
  prototype is the only tool that can derive global bounds for larger
  C programs while being as powerful as existing tools when deriving
  linear local bounds for tricky loop and recursion patterns.
\end{itemize}
\itemskip
%
\iffull{}
{\footnotesize \sl
[To the reviewers: The auxiliary material contains an anonymized
version of the extended article, and the source code of $\toolname$
and all examples.] }
